### 2023-06-21 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on BL figures
fixed fig 1
working on paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Formulation}Formulation}
%\todo[inline]{Changes to be made to Figure~\ref{fig:schematic}.}
%\begin{itemize}
%  \item Remove labels $\Gamma$, $\Omega$, $\gamma$
%  \item Line on vesicle is too thick and change color scheme to same as
%    Fig 2
%  \item Change to a confined geometry that we use (stenosis)
%  \item Show a couple of vesicle shapes and the parabolic profile at
%    the inlet, outlet, and in the middle
%\end{itemize}
\begin{figure}[H]
  \centering
%  \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
  \includegraphics[width=0.9\columnwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematic}\small A single multicomponent vesicle
  suspended in a strongly-confined stenosis. The color is the
  dimensionless stiffness which varies from $b_{\min} = 0.1$ to
  $b_{\max} = 1$. The vesicle dynamics are determined by a combination
  of phase, bending, and tension energies, and an imposed flow (blue
  arrows).}
%  \caption{\label{fig:schematic}\small A single multicomponent vesicle
%  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
%  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
%  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
%  are the ``floppy'' regions corresponding to the minimum bending
%  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
%  combination of phase, bending, and tension energies, and an imposed
%  flow on $\Gamma$. }
\end{figure}
We consider a single multicomponent vesicle $\omega$ with boundary
$\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with
boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid is assumed to
have zero Reynolds number and is therefore governed by the
incompressible Stokes equations
\begin{align}
    \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
        \quad \xx \in \Omega \backslash \gamma,
\end{align}
where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
we require that the velocity is continuous and locally inextensible, and
the membrane and hydrodynamic forces balance
\begin{align}
  \llbracket \uu \rrbracket = 0, \quad 
  \nabla_{\gamma} \cdot \uu = 0, \quad \xx \in \gamma, \quad
  \llbracket \TT\nn \rrbracket = \ff, 
\end{align}
where $\ff$ is the total membrane force and $\nn$ is the outward unit
normal of $\gamma$. By parameterizing $\gamma$ as $\xx(s,t)$, where $s$
is arclength and $t$ is time, the no-slip boundary condition is
$\frac{d\xx}{dt} = \uu(\xx)$.  Along the solid wall $\Gamma$, we impose
a Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
\begin{align}
  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constitutive equations}
Using the model first introduced by~\citet{liu-mar-li-vee-low2017}, and
then investigated further by~\citet{soh-tse-li-voi-low2010}, the
membrane forces depend on the Helfrich energy, line tension, and phase
energy. The phase and bending energies are coupled through the bending
modulus. In particular, the individual energies are
\begin{align}
  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \quad
  E_t = \int_{\gamma} \sigma \, ds, \\
  E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
  f(u) +\frac{\epsilon^2}{2}|\nabla_\gamma u|^2\right) \, ds,
  \label{eqn:PhaseEnergy}
\end{align}
where $u$ is the dimensionless lipid concentration, $b(u)$ is the
lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
$f(u) = \frac{1}{4}u^2(1-u)^2$ is a double-well potential with local
minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature
and $\ss$ is the tangent vector. We adopt the same setup
as~\citet{soh-tse-li-voi-low2010} where $\epsilon \ll 1$ is a
dimensionless parameter that controls the size of the transition region
of $u$, and $a$ is the dimensional line tension scaled by $b_{\max}/L$.
Both $\epsilon$ and $a$ are kept constant in all simulations. The
resulting membrane forces are
\begin{align}
  \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
    \left(b(u) \kappa^2 \ss\right)_s, \\
  \ff_t &= (\sigma \ss)_s, \\
  \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s.
\end{align}

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
$\beta \ll 1$, $Ca \gg 1$, or the vesicle is confined to a narrow
region. This behavior is demonstrated in Figure~\ref{fig:concModels}(a).
The stiff-to-floppy ratio is $\beta = 10^{-1}$. Using the linear bending
model~\eqref{eqn:linearBending}, the lipid concentration achieves a
maximum value of $u \approx 1.52$ which results in an instability that
is formed by a corresponding unphysical negative bending stiffness of
$b(u) \approx -0.5$. To rectify this issue, we parameterize the bending
modulus as
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, b(u) remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). This new bending model is validated in
Section~\ref{sec:validation}.
%To demonstrate the necessity of this new bending model, we consider a
%multicomponent vesicle in strong confinement with both bending
%models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
%stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
%model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
%maximum value of $u \approx 1.002$ which results in a minimum bending
%stiffness of $b(u) \approx \beta$. However, if we use the linear
%bending model~\eqref{eqn:linearBending}, the lipid concentration
%achieves a maximum value of $u \approx 1.52$ which results in an
%unphysical negative bending stiffness of $b(u) \approx -0.5$. The
%corresponding vesicle shape is in Figure~\ref{fig:concModels}(b), and
%the instability caused by the negative bending stiffness is near the
%region with negative curvature.

\begin{figure}[H]
  \centering
%  \input{figures/concModels.tikz} \\
%  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/OldBending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/concModels.pdf}
  \caption{\label{fig:concModels} \small (a) A multicomponent vesicle
  entering a closely-fitting channel using the linear
  model~\eqref{eqn:linearBending}. The vesicle bending modulus becomes
  negative, and this introduces an instability that first appears near
  the point with the largest negative curvature. (b) The linear bending
  model in red (equation~\eqref{eqn:linearBending}) and the new
  hyperbolic bending model in blue (equation~\eqref{eqn:tanhBending}).
  Note that the new bending model satisfies $b \in (\beta,1)$ even if $u
  \notin [0,1]$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:NumericalMethods}Numerical Methods}
We use a high-order integral equation formulation to resolve the complex
vesicle shapes. The velocity field $\uu$ is written as a combination of
a single-layer potential and a double-layer potential
\begin{align}
  \label{eqn:LPrep}
  \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
\end{align}
where
\begin{align}
  S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(
    -\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) \, ds_\yy, \\
%
    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} 
      \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
\end{align}
and $\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times
2$ identity matrix. To avoid tangling of the vesicle membrane, it is
parameterized in terms of the $\theta$-$L$
variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length
and $\theta$ is the opening angle of the tangent vector $\ss$. This
requires decomposing the velocity field on $\gamma$ into a normal
velocity $V$ and tangential velocity $T$. Then, the no-slip boundary
condition for the vesicle velocity is
\begin{align}
  \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
\end{align}
The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$
satisfies
\begin{align}
  \UU(\xx) = -\frac{1}{2}\eeta(\xx) + 
    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
  \label{eqn:DLP_BIE}
\end{align}

The vesicle and solid walls are discretized at a set of collocation
points. The single-layer potential is then approximated using quadrature
for weakly-singular integrands, while the double-layer potential is
approximated using the spectrally accurate trapezoid rule. Arclength
derivatives are computed with spectral accuracy using Fourier methods.
Time stepping is carried out using the second-order Adams-Bashforth
method. Finally, the resulting linear system is solved using GMRES.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
the tank treading and phase treading dynamics reported in the
literature. Figure~\ref{fig:treading} shows a tank treading (top) and a
phase treading (bottom) multicomponent vesicle in an unconfined shear
flow. These simulations align with the results reported
by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and 4).
\begin{figure}[H]
  \todo[inline]{Change to new color scheme.}
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent vesicle in a
  linear shear flow undergoes phase-treading (top) and tank-treading
  (bottom) with the new bending model~\eqref{eqn:tanhBending}. The red
  region is stiff and the blue region is floppy. The simulations
  qualitatively agree with the results presented
  by~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle under strong confinement}

The lubrication layer between a vesicle and the solid wall plays a
critical role on the vesicle's dynamics. Therefore, throughout
Section~\ref{sec:results}, we will calculate the size and analyze the
flow structure inside the lubrication layers. 
%We first justify the use of the term `lubrication layer' by verifying
%that the flow velocity is parabolic between the vesicle and the solid
%wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal
%velocity (solid line) and the corresponding best fit quadratic (dashed
%line) in the co-moving frame, and the profiles agree.
%
%\begin{figure}[H]
%    \centering
%    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
%    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
%    \label{fig:quadraticProof}
%\end{figure}
To define the size of the top lubrication layer (the size of the bottom
lubrication layer is defined similarly), we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between the vesicle
and the top half of the confining geometry.
%\begin{align}
%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
%\end{align}
%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$, where $\beta$
is a parameter. If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \beta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \beta$. Finally, the lubrication layer
width is
\begin{align}
    w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The width of the bottom lubrication layer, $w_\mathrm{bot}$ is
calculated by replacing $\Gamma_\mathrm{top}$ with
$\Gamma_\mathrm{bot}$.

%The terminology of boundary layer can be justified by computing the velocity field in the region between the vesicle and the solid wall. In Figure~\ref{fig:BkgrdFlow}, the co-moving velocity field around several different vesicle shapes that are observed in Section~\ref{sec:results} are illustrated. We have included plots of the horizontal velocity along a few vertical slices to demonstrate that a parabolic flow profile is observed.

The difference between the size of the top and lubrication layers is
closely related to the tank treading behavior of the vesicle. In cases
where the vesicle tank treads, we define the tank-treading velocity,
$\uu \cdot \ss$. To establish that a vesicle is tank treading, we verify
that the tangential velocity agrees at several points on $\gamma$.

@@

We also report the excess pressure for one of the geometries and relate
it to the size of the lubrication layers. Since we represent the
velocity with layer potentials~\eqref{eqn:LPrep}, the pressure at $\xx
\in \Omega$ is
\begin{align}
  p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
    \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} 
    \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) 
    \nn \cdot \eeta \, ds_\yy.
\end{align}
The excess pressure is the additional pressure that is required to pass
the vesicle through the geometry when compared to the pressure necessary
if the vesicle were absent. These pressure drops are defined by
subtracting the pressure at a point near the inlet and another near the
outlet. In our formulation, because of the order of subtraction, the
excess pressure is always negative.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Formulation}Formulation}
%\todo[inline]{Changes to be made to Figure~\ref{fig:schematic}.}
%\begin{itemize}
%  \item Remove labels $\Gamma$, $\Omega$, $\gamma$
%  \item Line on vesicle is too thick and change color scheme to same as
%    Fig 2
%  \item Change to a confined geometry that we use (stenosis)
%  \item Show a couple of vesicle shapes and the parabolic profile at
%    the inlet, outlet, and in the middle
%\end{itemize}
\begin{figure}[H]
  \centering
%  \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
  \includegraphics[width=0.9\columnwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematic}\small A single multicomponent vesicle
  suspended in a strongly-confined stenosis. The color is the
  dimensionless stiffness which varies from $b_{\min} = 0.1$ to
  $b_{\max} = 1$. The vesicle dynamics are determined by a combination
  of phase, bending, and tension energies, and an imposed flow (blue
  arrows).}
%  \caption{\label{fig:schematic}\small A single multicomponent vesicle
%  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
%  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
%  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
%  are the ``floppy'' regions corresponding to the minimum bending
%  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
%  combination of phase, bending, and tension energies, and an imposed
%  flow on $\Gamma$. }
\end{figure}
We consider a single multicomponent vesicle $\omega$ with boundary
$\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with
boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid is assumed to
have zero Reynolds number and is therefore governed by the
incompressible Stokes equations
\begin{align}
    \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
        \quad \xx \in \Omega \backslash \gamma,
\end{align}
where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
we require that the velocity is continuous and locally inextensible, and
the membrane and hydrodynamic forces balance
\begin{align}
  \llbracket \uu \rrbracket = 0, \quad 
  \nabla_{\gamma} \cdot \uu = 0, \quad
  \llbracket \TT\nn \rrbracket = \ff, \quad \xx \in \gamma,
\end{align}
where $\ff$ is the total membrane force and $\nn$ is the outward unit
normal of $\gamma$. Parameterizing $\gamma$ as $\xx(s,t)$, where $s$ is
arclength and $t$ is time, the no-slip boundary condition is
$\frac{d\xx}{dt} = \uu(\xx)$. Along the solid wall $\Gamma$, we impose a
Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
\begin{align}
  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constitutive equations}
Using the model first introduced by~\citet{liu-mar-li-vee-low2017}, the
membrane forces depend on the Helfrich energy, line tension, and phase
energy. The phase and bending energies are coupled through the bending
modulus. In particular, the individual energies are
\begin{align}
  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \quad
  E_t = \int_{\gamma} \sigma \, ds, \\
  E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
  f(u) +\frac{\epsilon^2}{2}|\nabla_\gamma u|^2\right) \, ds,
  \label{eqn:PhaseEnergy}
\end{align}
where $u$ is the dimensionless lipid concentration, $b(u)$ is the
lipid-dependent bending modulus, $\sigma$ is the vesicle's tension,
$\kappa$ is the membrane curvature, and $f(u) = \frac{1}{4}u^2(1-u)^2$
is a double-well potential with local minimums at $u=0$ and $u=1$. The
parameter $\epsilon \ll 1$ sets the size of the transition region of
$u$, and the parameter $a$ is line tension scaled by the characteristic
bending stiffness. Both $\epsilon$ and $a$ are kept constant in all
simulations. The resulting membrane forces are
\begin{align}
  \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
    \left(b(u) \kappa^2 \ss\right)_s, \\
  \ff_t &= (\sigma \ss)_s, \\
  \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s,
\end{align}
where $\ss$ is the unit tangent vector of $\gamma$.

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
$\beta \ll 1$, $Ca \gg 1$, or the vesicle is confined to a narrow
region. This behavior is demonstrated in Figure~\ref{fig:concModels}(a)
for a vesicle with a floppy-to-stiff ratio $\beta = 10^{-1}$. Using the
linear bending model~\eqref{eqn:linearBending}, the lipid concentration
achieves a maximum value of $u \approx 1.5$ which results in an
instability that is formed by a corresponding unphysical negative
bending stiffness of $b(u) \approx -0.5$. To rectify this issue, we
parameterize the bending modulus as
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, b(u) remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). This new bending model is validated in
Section~\ref{sec:validation}.
%To demonstrate the necessity of this new bending model, we consider a
%multicomponent vesicle in strong confinement with both bending
%models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
%stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
%model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
%maximum value of $u \approx 1.002$ which results in a minimum bending
%stiffness of $b(u) \approx \beta$. However, if we use the linear
%bending model~\eqref{eqn:linearBending}, the lipid concentration
%achieves a maximum value of $u \approx 1.52$ which results in an
%unphysical negative bending stiffness of $b(u) \approx -0.5$. The
%corresponding vesicle shape is in Figure~\ref{fig:concModels}(b), and
%the instability caused by the negative bending stiffness is near the
%region with negative curvature.

\begin{figure}[H]
  \centering
%  \input{figures/concModels.tikz} \\
%  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/OldBending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/concModels.pdf}
  \caption{\label{fig:concModels} \small (a) A multicomponent vesicle
  entering a closely-fitting channel (black lines) using the linear
  model~\eqref{eqn:linearBending}. An instability is introduced where
  the vesicle bending modulus becomes negative. (b) The linear bending
  model in red (equation~\eqref{eqn:linearBending}) and the new
  hyperbolic bending model in blue (equation~\eqref{eqn:tanhBending}).
  Note that the new bending model satisfies $b \in (\beta,1)$ even if $u
  \notin [0,1]$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:NumericalMethods}Numerical Methods}
We use a high-order integral equation formulation to resolve the complex
vesicle shapes and long-range hydrodynamic interactions. The velocity
field $\uu$ is written as a combination of a single-layer potential and
a double-layer potential
\begin{align}
  \label{eqn:LPrep}
  \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
\end{align}
where
\begin{align}
  S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(
    -\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) \, ds_\yy, \\
%
    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} 
      \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
\end{align}
and $\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times
2$ identity matrix. To avoid tangling of the vesicle membrane, it is
parameterized in terms of the $\theta$-$L$
variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length
and $\theta$ is the opening angle of the tangent vector $\ss$. This
requires decomposing the velocity field on $\gamma$ into a normal
velocity $V$ and tangential velocity $T$. Then, the no-slip boundary
condition for the vesicle velocity is
\begin{align}
  \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
\end{align}
The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$
satisfies
\begin{align}
  \UU(\xx) = -\frac{1}{2}\eeta(\xx) + 
    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
  \label{eqn:DLP_BIE}
\end{align}

The vesicle and solid walls are discretized at a set of collocation
points. The single-layer potential is then approximated using quadrature
for weakly-singular integrands, while the double-layer potential is
approximated using the spectrally accurate trapezoid rule. Arclength
derivatives are computed with spectral accuracy using Fourier methods.
The resulting linear system is solved using GMRES. Finally, time
stepping is carried out using the second-order Adams-Bashforth method.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
the dynamics reported in the literature. Figure~\ref{fig:treading} shows
a phase treading (top) ajnd a tank treading (bottom) multicomponent
vesicle in an unconfined shear flow. These simulations align with the
results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and
4).
\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent vesicle in a
  linear shear flow undergoes phase-treading (top) and tank-treading
  (bottom) with the new bending model~\eqref{eqn:tanhBending}. The red
  region is stiff and the blue region is floppy. The simulations
  qualitatively agree with the results presented
  by~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:LL} Lubrication layers and excess pressure}
The lubrication layer between a vesicle and the solid wall plays a
critical role on the vesicle's dynamics. Therefore, throughout
Section~\ref{sec:results}, we calculate the size and analyze the flow
inside the lubrication layers. 
%We first justify the use of the term `lubrication layer' by verifying
%that the flow velocity is parabolic between the vesicle and the solid
%wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal
%velocity (solid line) and the corresponding best fit quadratic (dashed
%line) in the co-moving frame, and the profiles agree.
%
%\begin{figure}[H]
%    \centering
%    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
%    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
%    \label{fig:quadraticProof}
%\end{figure}
To define the size of the top lubrication layer (the size of the bottom
lubrication layer is defined similarly), we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point on
the vesicle, $\xx \in \gamma$, and the top half of the confining
geometry.
%\begin{align}
%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
%\end{align}
%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where $\delta$
is a parameter. If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \delta$. Finally, the lubrication layer
width is
\begin{align}
    w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} 
      \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
%The width of the bottom lubrication layer, $w_\mathrm{bot}$ is
%calculated by replacing $\Gamma_\mathrm{top}$ with
%$\Gamma_\mathrm{bot}$.

%The terminology of boundary layer can be justified by computing the
%velocity field in the region between the vesicle and the solid wall. In
%Figure~\ref{fig:BkgrdFlow}, the co-moving velocity field around several
%different vesicle shapes that are observed in Section~\ref{sec:results}
%are illustrated. We have included plots of the horizontal velocity
%along a few vertical slices to demonstrate that a parabolic flow
%profile is observed.

A difference between the size of the top and lubrication layers
indicates that the vesicle is off-centered from the center of the
channel, and this results in tank-treading behavior~\cite{aga-bir2020}.
To determine if a vesicle is tank-treading, we calculate the tangential
velocity at several points on $\gamma$, and if this value is constant,
this is the tank-treading velocity.

@@

We also report the excess pressure for one of the geometries and relate
it to the size of the lubrication layers. The excess pressure is the
additional pressure that is required to pass the vesicle through the
geometry when compared to the pressure necessary if the vesicle were
absent. These pressure calculations are taken near the inlets and
outlets of the confining geometry, and the vesicle itself is never near
these locations. Since we use a layer potential formulation, the
pressure at $\xx \in \Omega$ is
\begin{align}
  p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
    \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} 
    \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) 
    \nn \cdot \eeta \, ds_\yy.
\end{align}
%These pressure drops are defined by
%subtracting the pressure at a point near the inlet and another near the
%outlet. In our formulation, because of the order of subtraction, the
%excess pressure is always negative.
